\section{Key Projects}
\vspace{0.3cm}

\begin{itemize}[leftmargin=0.0in]
    \setlength\itemsep{.2em}
%  Project with AL-Garady: Image Processing 
    % \vspace{0.5cm}
    % \cventry{Righ-Bottom}{Subtitle}{Title}{Rith-Top}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.3em}
    % \item Item
    % \item Item
    % }


    \cventry{}{\link{https://github.com/nagiurDev/news-classification}}{News Classification}{\textbf{NLP, Web Scraping, Data Preprocessing, ML}}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.3em}
    \vspace{5pt}
    \item Scrapes news data from People.cn.
    \item Cleans, preprocesses, and explores the news data.
    \item Builds and evaluates an SVM model for news classification.
    \item Uses Jupyter notebooks for data processing and model building.
    }

    \vspace{0.5cm}
    \cventry{}{\link{https://github.com/nagiurDev/DELF-image-search}}{DELF Image Search}{CV, DELF , Image Search, ML}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.3em}
    \vspace{5pt}
    \item This project performs image similarity search using the TensorFlow Hub DELF module.
    \item It leverages DELF's powerful feature extraction for accurate image comparisons.
    \item The code is structured for modularity, testability, and easy extension.
    }

    \vspace{0.5cm}
    \cventry{}{\link{https://github.com/nagiurDev/historical-photo-restoration-ESRGAN}}{Historical Photo Restoration with ESRGAN}{\textbf{CV, ESRGAN, Image Restoration, ML}}{}
    { \setlength{\itemindent}{.2in} \setlength\itemsep{.3em}
        \vspace{5pt}
        \item Restored degraded historical photographs using a fine-tuned ESRGAN deep learning model.
        \item Improved image quality significantly. %, achieving X\% increase in PSNR and Y\% in SSIM.
        \item Successfully addressed common degradations like noise, scratches, and fading.
    }

    \vspace{0.5cm}
    \cventry{}{\link{https://github.com/nagiurDev/parking-spot-dataset}}{Parking Spot Detection Dataset}{\textbf{CV, Object Detection, YOLO, ML}}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.3em}
    \vspace{5pt}
    \item Creates a parking spot detection dataset from video.
    \item Includes annotated images for YOLO model training.
    \item Provides preprocessing scripts, augmentation, and evaluation tools.
    \item Dataset organized in YOLO format (train/validation/test).
    }

    \vspace{0.5cm}
    \cventry{}{\link{https://github.com/nagiurDev/sst2-sentiment-analysis-comparison}}{SST-2 Sentiment Analysis Comparison}{\textbf{NLP, Fine-tuning, Benchmarking, ML}}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.3em}
    \vspace{5pt}
    \item Compares BERT, DistilBERT, and RoBERTa for sentiment analysis.
    \item Uses the SST-2 dataset for benchmarking.
    \item Evaluate performance using accuracy and F1-score.
    \item Provides code and results for reproducibility.
    }


    
\end{itemize}


