\section{Key Projects}
\vspace{0.3cm}

\begin{itemize}[leftmargin=0.0in]
    \setlength\itemsep{.2em}

    \cventry{}{ \link{https://github.com/nagiurDev/grammar-sentiment-emotion-analysis} }{Fine-tuning Pre-trained for Writing Improvement}{\textbf{NLP, transformer}}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.3em}
    \vspace{5pt}
    \item \textbf{Datasets:} CoLA, Lang-8, SST-2, GoEmotions
    \item \textbf{Models:} RoBERTa (base), FLAN-T5 (base)
    \item \textbf{Challenges:} Optimizing pipeline for multiple, potentially conflicting objectives.
    \item \textbf{Key achievements:} Balancing task-specific optimization in multi-task learning.
    }
    
% 

    \cventry{}{\link{https://github.com/nagiurDev/news-classification}}{News Classification}{\textbf{NLP, Web Scraping, Data Preprocessing}}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.3em}
    \vspace{5pt}
    \item Scrapes news data from People.cn.
    \item Cleans, preprocesses, and explores the news data.
    \item Builds and evaluates an SVM model for news classification.
    \item Uses Jupyter notebooks for data processing and model building.
    }

    % \vspace{0.5cm}
    % \cventry{}{\link{https://github.com/nagiurDev/DELF-image-search}}{DELF Image Search}{CV, DELF , Image Search, ML}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.3em}
    % \vspace{5pt}
    % \item This project performs image similarity search using the TensorFlow Hub DELF module.
    % \item It leverages DELF's powerful feature extraction for accurate image comparisons.
    % \item The code is structured for modularity, testability, and easy extension.
    % }


    \vspace{0.5cm}
    \cventry{}{\link{https://github.com/nagiurDev/sst2-sentiment-analysis-comparison}}{SST-2 Sentiment Analysis Comparison}{\textbf{NLP, Fine-tuning, Benchmarking}}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.3em}
    \vspace{5pt}
    \item Compares BERT, DistilBERT, and RoBERTa for sentiment analysis.
    \item Uses the SST-2 dataset for benchmarking.
    \item Evaluate performance using accuracy and F1-score.
    \item Provides code and results for reproducibility.
    }


    
\end{itemize}


